### 2015-08-25 books/Logic_of_Political_Survival_Mesquita/code/ch41.tex
-

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('bdm2s2_nation_year_data_may2002.csv')
df['Klepto'] = (df['TAXGDP']-df['Expenditure']).abs()
df = df[['regyr','ccode','aid_gdp','lrgdpc','pop','year','W','S','Klepto','laglrgdpc']]
\end{minted}

>>>>

%%%%%%%% Run these first %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('../bdm2s2_nation_year_data_may2002.csv')
print list(df.columns)
\end{minted}

\begin{verbatim}
['Unnamed: 0', 'year', 'AGEA', 'AGEI', 'AUT', 'BRITCOL', 'CATH', 'COMEX',
'EDT', 'EDTG', 'ELF60', 'ETHNIC', 'GINI', 'GXPDEDUC', 'GXPDHLTH',
'GXPDSSEC', 'GXPKTOTL', 'INEQ', 'INST', 'LEGSELEC', 'MOSLEM', 'OIL',
'PROT', 'REGION', 'REGION2', 'RELIGION', 'RIOTS', 'STRIKES', 'UNSTABLE',
'WAR', 'ccode', 'TAXGDP', 'TAXGNP', 'TREV', 'PRIVCON', 'INCOMEY',
'INCOMET', 'DIRT', 'INDIRT', 'democ', 'autoc', 'polity', 'polity2',
'durable', 'xrreg', 'xrcomp', 'xropen', 'xconst', 'parreg', 'parcomp',
'exrec', 'exconst', 'polcomp', 'bdate', 'bprec', 'change', 'd3', 'sf',
'regtrans', 'country', 'BANKScode', 'Radios', 'Newspapers', 'Assinations',
'GenStrikes', 'GovCrises', 'Purges', 'Riots', 'Revolutions', 'AntiGovDem',
'ConflictIndex', 'RegimeType', 'Coups', 'HeadofState', 'Guerilla',
'RegisteredVoters', 'MajConstChg', 'Premier', 'Legselec', 'NatGovRevenue',
'NatGovExpend', 'defenseovertotal', 'name', 'chcode', 'longname',
'coding_differs', 'WorldBankCode', 'WorldBankName', 'fatlev1', 'hostlev1',
'legselec', 'esolow', 'bhkavg', 'exchprem', 'sh_staa', 'sh_med_b',
'sh_med_p', 'sh_h2o_s', 'immig', 'emig', 'ID', 'NAME', 'PR', 'CL', 'cap',
'milper', 'milex', 'energy', 'irst', 'majpow', 'warnoEX', 'EXdeaths',
'EXintside', 'EXinitiate', 'sysstat', 'EX_war_start', 'EXduration',
'EX_WAR', 'number_of_EXwars', 'biggestEXwar', 'warno', 'duration',
'deaths', 'outcome', 'initiate', 'is_war_start', 'IS_WAR',
'number_of_ISwars', 'biggestISwar', 'warnoCL', 'CLdeaths', 'CLintside',
'CLinitiate', 'CL_war_start', 'CLduration', 'CL_WAR', 'number_of_CLwars',
'biggestCLwar', 'ai', 'sd', 'ainew', 'sdnew', 'idgurr', 'worldbankcode',
'WB_pop', 'WB_gdppc_constUS95', 'WB_growth', 'WB_gdp_curUS', 'WB_gdp95',
'Aid_pcUS', 'FemSec', 'Doctors', 'MilPerson', 'MilEx', 'MilExGNI',
'InfMort', 'LowBirth', 'LifeExp', 'Labor_PrimEd', 'ImmuneMEASLES',
'ImmuneDPT', 'Illiteracy', 'Beds', 'HealthEXP', 'HealthExpPPP',
'GrossNatSaving', 'GrossDomSaving', 'Capital_formation', 'Saving_dom',
'FDI', 'Foreign_Finnace', 'ConsumptionSpending', 'Expenditure',
'Deathrate', 'newspaper', 'HealthExpend', 'EducExpend',
'CapitalExpend_tot', 'CurRevenue', 'GrossDomInvest', 'GovDebt',
'Birthrate', 'total_aid', 'aid_cap_constUS', 'aid_gdp', 'CapitalExpend',
'pop', 'rgdpch', 'rgdpl', 'c', 'i', 'g', 'rgdptt', 'y', 'cgdp', 'cc', 'ci',
'cg', 'p', 'pc', 'pi', 'pg', 'xr', 'rgdpea', 'rgdpw', 'kapw', 'kdur',
'knres', 'kother', 'kres', 'ktranp', 'open', 'rgnp', 'ipri', 'stliv',
'finittrm', 'yrcurnt', 'military', 'auton', 'eda', 'strikes', 'nspolpr',
'agovdem', 'govtcris', 'corrupti80_89', 'purges', 'coups', 'riots',
'constchg', 'cabchg', 'genocide', 'worldbankname', 'NatYr', 'cowreg',
'regyr', 'demaut', 'lpop', 'lpop_WB', 's', 'S', 'W', 'W_extend', 'W_mod',
'polityW', 'polityWn', 'Parl_Pres', 'w2', 'demaut2', 'WoverS', 'dbigw',
'dW', 'dw30', 'lagW', 'lagW2', 'dwos30', 'grow', 'LongGR1', 'LongGR2',
'LongGR3', 'LongGR4', 'lagGrow', 'lrgdpc', 'laglrgdpc', 'lgdpWB',
'laglgdpWB', 'VarGrow', 'VarGrow_', 'build', 'bal_bud', 'VarBud',
'Var_bud', 'Klepto', 'nexcap'] 
\end{verbatim}

\begin{minted}[fontsize=\footnotesize]{python}
df['polchange'] = (df.W-df.shift(2).W)**2
df['DW20'] = df.W-df.shift(2).W
df['Klepto'] = (df['TAXGDP']-df['Expenditure']).abs()
\end{minted}

\begin{minted}[fontsize=\footnotesize]{python}
import statsmodels.formula.api as smf
results = smf.ols('WB_growth ~ W + S + DW20 + polchange', data=df).fit()
print results.summary()
\end{minted}

\begin{verbatim}
                            OLS Regression Results                            
==============================================================================
Dep. Variable:              WB_growth   R-squared:                       0.003
Model:                            OLS   Adj. R-squared:                  0.003
Method:                 Least Squares   F-statistic:                     4.266
Date:                Tue, 25 Aug 2015   Prob (F-statistic):            0.00190
Time:                        16:41:42   Log-Likelihood:                -16242.
No. Observations:                4985   AIC:                         3.249e+04
Df Residuals:                    4980   BIC:                         3.253e+04
Df Model:                           4                                         
Covariance Type:            nonrobust                                         
==============================================================================
                 coef    std err          t      P>|t|      [95.0% Conf. Int.]
------------------------------------------------------------------------------
Intercept      4.2384      0.259     16.382      0.000         3.731     4.746
W             -0.3539      0.364     -0.972      0.331        -1.068     0.360
S             -0.3540      0.331     -1.069      0.285        -1.003     0.295
DW20           0.6777      0.620      1.093      0.274        -0.538     1.893
polchange     -3.8690      1.014     -3.817      0.000        -5.856    -1.882
==============================================================================
Omnibus:                     1170.985   Durbin-Watson:                   1.341
Prob(Omnibus):                  0.000   Jarque-Bera (JB):            61520.180
Skew:                           0.155   Prob(JB):                         0.00
Kurtosis:                      20.207   Cond. No.                         16.9
==============================================================================

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('bdm2s2_nation_year_data_may2002.csv')
df = df[['regyr','ccode','aid_gdp','lrgdpc','pop','year','W','S','Klepto','laglrgdpc']]
\end{minted}
